Modul Praktikum Minggu 3

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu III/M3SK003 Mohammad Rizka Fadhli 20921004.Rmd
re arrange folder

---
title: "Modul Praktikum Minggu 3"
author: "Mohammad Rizka Fadhli - 20921004"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/S2 Sains Komputasi ITB/Kuliah/Semester I/Pemrograman dalam Sains/Tugas/Minggu III")
rm(list=ls())

>>>>

---
title: "Modul Praktikum Minggu 3"
author: "Mohammad Rizka Fadhli - 20921004"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/209_ITB/Semester I/Pemrograman dalam Sains/Minggu III")
rm(list=ls())
